Tables/Graphs for Article

### 2017-11-26 article submission/draft1.Rnw
added univariate analysis tables

\documentclass{article}

\begin{document}
\SweaveOpts{concordance=TRUE}

@@

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)

# -------------------------------------------------------------------------------
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

@@

@@

<<include = FALSE>>=
answered <- sum(x$answered)
percentans <- round((answered / nrow(x)) * 100, 1) 
shortest <- round(min(x$time_until_answer) * 60, 2) 
longest <- round(max(x$time_until_answer), 2)
longest_d <- round(longest / 24, 2) 
@

@@

@@

<<include = FALSE>>=
surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
stats <- summary(KM)$table
mean <- round(unname(stats[5]), 2) 
median <- round(unname(stats[7]), 2)
@

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Fri Nov 24 17:16:56 2017
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
  Percent \\ Answered & Time (hours) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\label{table:quantiles}
\end{table}

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table ~\ref{table:quantiles} provides additional percentiles of survival time.

As the distributions of continuous predictors were extremely right-skewed, the following transformations were applied:

Log transformation
\begin{itemize}
  \item number of characters in a question's text
\end{itemize}

Square root transformations
\begin{itemize}
  \item The average score of a question's tags.
  \item The average number of characters in a question's tags.
  \item The number of characters in a question's user-defined device name.
  \item The ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

Predictors with p-values less than 0.01 are shown in Table b. All transformed continuous and categorical predictors were entered into the full model for cross-validation. Average performance metrics for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The following restricted cubic splines were applied continuous variables:

4 knots
\begin{itemize}
  \item number of characters in the user-defined device name
\end{itemize}

3 knots
\begin{itemize}
  \item number of characters in a question's text
  \item square root of the average number of characters in a question's tags
  \item ratio of number of line breaks to the number of characters in a question's text
\end{itemize}

>>>>

\documentclass{article}
\usepackage{multirow}
\begin{document}
\SweaveOpts{concordance=TRUE}

@@

model <- rms::cph(survival::Surv(time_until_answer, answered) ~ new_category + new_user + contain_unanswered + contain_answered + title_questionmark + text_contain_punct + text_all_lower + update + prior_effort + sqrt(avg_tag_score) + log10(text_length) + rms::rcs(sqrt(device_length), 4) + rms::rcs(sqrt(avg_tag_length), 3) + rms::rcs(sqrt(newline_ratio), 3), data = x, x = TRUE, y = TRUE, surv = TRUE)
@

@@

<< echo = FALSE >>=
set.seed(444)
splitPlan <- vtreat::kWayCrossValidation(nrow(x), 5, NULL, NULL)

@@

@@

<< echo = FALSE >>=
answered <- sum(x$answered)
percentans <- round((answered / nrow(x)) * 100, 1) 
shortest <- round(min(x$time_until_answer) * 60, 2) 
longest <- round(max(x$time_until_answer), 2)
longest_d <- round(longest / 24, 2) 
@

@@

<< echo = FALSE >>=
surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
stats <- summary(KM)$table
mean <- round(unname(stats[5]), 2) 
median <- round(unname(stats[7]), 2)
@

\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 Percent\\ Answered & Time (hrs) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Table of Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

\begin{table}[ht]
\centering
\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  Log transformation of the number of characters in a question's text* & 0.00 \\ 
  \hline
  Square root transformation of the number of characters in a question's text* & 0.00 \\ 
  \hline
  Number of characters in a question's text (untransformed) & 0.00 \\
  \hline
  Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text* & 0.00 \\ 
  \hline
  Square root transformation of the average frequency ``score'' of a question's tags* & 0.00 \\ 
  \hline
  Average frequency ``score'' of a question's tags (untransformed) & 0.00 \\ 
  \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 0.00 \\ 
  \hline
  Square root transformation of the number of characters in the user-defined device title* & 0.00 \\ 
  \hline
  Square root transformation of the average number of characters in a question's tags* & 0.00 \\ 
  \hline
  Number of characters in the user-defined device title (untransformed) & 0.01 \\ 
  \hline
  Average number of characters in a question's tags (untransformed) & 0.03 \\ 
   \hline
\end{tabular}
\label{table:qresults}
\end{table}

\begin{table}[ht]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 0.00 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
  \hline
  Day of the week the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's text is in all lower case & 0.00 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors were entered into the full model. Restricted cubic splines were fit to all * quantitative variables.

\begin{table}[ht]
\centering
\caption{Determining the optimal k number of splines for each predictor} 
\begin{tabular}{| p{5cm} | l | l | l |}
  \hline
  Predictor & K & p-value & AIC \\ 
  \hline
  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
  & 0 & 0.00 & 65862.83 \\ 
  & 5* & 0.00 & 65862.02 \\ 
  & 4 & 0.00 & 65863.35 \\ 
  & 3 & 0.00 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
  & 0 & 0.00 & 65890.28 \\ 
  & 5 & 0.00 & 65884.70 \\ 
  & 4 & 0.00 & 65882.98 \\ 
  & 3* & 0.00 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
  & 0* & 0.00 & 65890.75 \\ 
  & 5 & 0.00 & 65891.69 \\ 
  & 4 & 0.00 & 65891.75 \\ 
  & 3 & 0.00 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
  & 0 & 0.00 & 65922.76 \\ 
  & 5* & 0.00 & 65853.56 \\ 
  & 4 & 0.00 & 65882.07 \\ 
  & 3 & 0.00 & 65881.39 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
  & 0 & 0.00 & 65923.26 \\ 
  & 5 & 0.00 & 65912.11 \\ 
  & 4* & 0.00 & 65910.10 \\ 
  & 3 & 0.00 & 65912.38 \\ 
   \hline
\end{tabular}
\label{table:splines}
\end{table}

Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model for cross-validation.

Average performance metrics for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The following restricted cubic splines were applied continuous variables:

### 2017-11-26 article submission/draft1.tex
added univariate analysis tables

\documentclass{article}

\usepackage{Sweave}
\begin{document}
\input{draft1-concordance}

@@

\begin{Schunk}
\begin{Sinput}
> answered <- sum(x$answered)
> percentans <- round((answered / nrow(x)) * 100, 1) 
> shortest <- round(min(x$time_until_answer) * 60, 2) 
> longest <- round(max(x$time_until_answer), 2)
> longest_d <- round(longest / 24, 2) 
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
> surv_object <- survival::Surv(x$time_until_answer, x$answered, type = "right")
> KM <- survival::survfit(surv_object ~ 1, conf.type = "log-log")
> stats <- summary(KM)$table
> mean <- round(unname(stats[5]), 2) 
> median <- round(unname(stats[7]), 2)
\end{Sinput}
\end{Schunk}

% latex table generated in R 3.4.1 by xtable 1.8-2 package
% Fri Nov 24 17:16:56 2017
\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
  Percent \\ Answered & Time (hours) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\label{table:quantiles}
\end{table}

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table ~\ref{table:quantiles} provides additional percentiles of survival time.

As the distributions of continuous predictors were extremely right-skewed, the following transformations were applied:

Log transformation
\begin{itemize}
  \item number of characters in a question's text
\end{itemize}

Square root transformations
\begin{itemize}
  \item The average score of a question's tags.
  \item The average number of characters in a question's tags.
  \item The number of characters in a question's user-defined device name.
  \item The ratio of the number of line breaks to the number of characters in the question's text.
\end{itemize}

Predictors with p-values less than 0.01 are shown in Table b. All transformed continuous and categorical predictors were entered into the full model for cross-validation. Average performance metrics for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The following restricted cubic splines were applied continuous variables:

4 knots
\begin{itemize}
  \item number of characters in the user-defined device name
\end{itemize}

3 knots
\begin{itemize}
  \item number of characters in a question's text
  \item square root of the average number of characters in a question's tags
  \item ratio of number of line breaks to the number of characters in a question's text
\end{itemize}

>>>>

\documentclass{article}
\usepackage{multirow}
\usepackage{Sweave}
\begin{document}
\input{draft1-concordance}

@@

@@

\begin{table}[ht]
\centering
\begin{tabular}{rlr}
  \hline
 Percent\\ Answered & Time (hrs) \\ 
  \hline
  25 & 0.88 \\ 
  50 & 9.16 \\ 
  55 & 18.38 \\ 
  58 & 33.71 \\ 
  60 & 59.47 \\ 
  64 & 683.19 \\ 
   \hline
\end{tabular}
\caption{Table of Kaplan-Meier estimated quantiles of survival time}
\label{table:quantiles}
\end{table}

  Figure  ~\ref{fig:kmcurve} shows the Kaplan-Meier curve of survival probability for all questions in the data. The curve indicates that around 150 hours after a question has been posted, survival probability coasts at around 0.35 and never reaches 0, indicating that if a question does not receive an answer within the first 100 hours, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours. Table \ref{table:quantiles} provides additional percentiles of survival time.

\begin{table}[ht]
\centering
\caption{Univariate analysis results for quantitative predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
  Predictor & p-value \\ 
  \hline \hline
  Log transformation of the number of characters in a question's text* & 0.00 \\ 
  \hline
  Square root transformation of the number of characters in a question's text* & 0.00 \\ 
  \hline
  Number of characters in a question's text (untransformed) & 0.00 \\
  \hline
  Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text* & 0.00 \\ 
  \hline
  Square root transformation of the average frequency ``score'' of a question's tags* & 0.00 \\ 
  \hline
  Average frequency ``score'' of a question's tags (untransformed) & 0.00 \\ 
  \hline
  Ratio of the number of line breaks to the number of characters in a question's text (untransformed) & 0.00 \\ 
  \hline
  Square root transformation of the number of characters in the user-defined device title* & 0.00 \\ 
  \hline
  Square root transformation of the average number of characters in a question's tags* & 0.00 \\ 
  \hline
  Number of characters in the user-defined device title (untransformed) & 0.01 \\ 
  \hline
  Average number of characters in a question's tags (untransformed) & 0.03 \\ 
   \hline
\end{tabular}
\label{table:qresults}
\end{table}

\begin{table}[ht]
\centering
\caption{Univariate analysis results for categorical predictors, ordered by increasing p-values} 
\begin{tabular}{|p{12cm}|p{2cm}|}
  \hline
 Predictor & p-value \\ 
  \hline \hline
  Device category & 0.00 \\
  \hline
  Whether or not the user had been a member for less than one day before the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's title ended in a questionmark & 0.00 \\ 
  \hline
  Whether or not the question's text contained at least one end punctuation mark & 0.00 \\ 
  \hline
  Day of the week the question was posted & 0.00 \\ 
  \hline
  Whether or not the question's text is in all lower case & 0.00 \\ 
  \hline
  Whether or not the user made an effort to solve the problem on their own, prior to asking the question & 0.00 \\ 
  \hline
  Whether or not the user edited or added information to the question's text sometime after posting it & 0.00 \\
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
  \hline
  Whether or not the question's title contains terms considered to be frequently used among unanswered questions & 0.00 \\ 
   \hline
\end{tabular}
\label{table:cresults}
\end{table}

Results of univariate analyis for transformed and untransformed quantitative predictors, and categorical predictors, are are shown in Table \ref{table:qresults} and Table \ref{table:cresults}, respectively. All categorical predictors were entered into the full model. Restricted cubic splines were fit to all * quantitative variables.

\begin{table}[ht]
\centering
\caption{Determining the optimal k number of splines for each predictor} 
\begin{tabular}{| p{5cm} | l | l | l |}
  \hline
  Predictor & K & p-value & AIC \\ 
  \hline
  \multirow{ 4 }{ 5cm }{Log transformation of the number of characters in a question's text} 
  & 0 & 0.00 & 65862.83 \\ 
  & 5* & 0.00 & 65862.02 \\ 
  & 4 & 0.00 & 65863.35 \\ 
  & 3 & 0.00 & 65862.08 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the ratio of the number of line breaks to the number of characters in a question's text}
  & 0 & 0.00 & 65890.28 \\ 
  & 5 & 0.00 & 65884.70 \\ 
  & 4 & 0.00 & 65882.98 \\ 
  & 3* & 0.00 & 65881.93 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average frequency ``score'' of a question's tags}
  & 0* & 0.00 & 65890.75 \\ 
  & 5 & 0.00 & 65891.69 \\ 
  & 4 & 0.00 & 65891.75 \\ 
  & 3 & 0.00 & 65892.35 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the number of characters in the user-defined device title}
  & 0 & 0.00 & 65922.76 \\ 
  & 5* & 0.00 & 65853.56 \\ 
  & 4 & 0.00 & 65882.07 \\ 
  & 3 & 0.00 & 65881.39 \\ 
  \hline
  \multirow{ 4 }{ 5 cm }{Square root transformation of the average number of characters in a question's tags}
  & 0 & 0.00 & 65923.26 \\ 
  & 5 & 0.00 & 65912.11 \\ 
  & 4* & 0.00 & 65910.10 \\ 
  & 3 & 0.00 & 65912.38 \\ 
   \hline
\end{tabular}
\label{table:splines}
\end{table}

Table \ref{table:splines} shows the results of determining the optimal number of knots for each quantitative predictor. Knots marked * were included in the final model for cross-validation.

Average performance metrics for test and training sets, found in table c, were considerably low. However, metrics did not change substantially from training to test sets, indicating that the model does not overfit. The following restricted cubic splines were applied continuous variables:
